Paper 2 !DRAFT! Do not circulate!

### 2014-08-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Paper2 now includes a second graph of historical data. New graph has different faceting, thereby allowing more-direct comparison of different sources.

Figure~\ref{fig:Historical_Data} shows a graph of historical data.

<<Historical_Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.">>=
historicalPlot(historicalData, 
               facet_formula = Country ~ Source, 
               lines_formula = iGDP + iK + iL + iXp + iXf + iU ~ Year, 
               line_types = c(1,2,3,4,5,6)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@

>>>>

Figure~\ref{fig:Historical_Data_1} shows a graph of historical data.

<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
mdata <- melt(historicalData, 
              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
              variable.name = "variable",
              value.name = "value")
historicalPlot(mdata, 
               facet_formula = Country ~ Source, 
               lines_formula = variable + value ~ Year, 
               line_types = c(1,2,3,4,5,6)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@

Figure~\ref{fig:Historical_Data_2} shows the same data in a different form.

<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
historicalPlot(mdata, 
               facet_formula=Country~variable, 
               lines_formula=Source+value~Year, 
               line_types=c(1,2,3)) +  
  xlab("") + 
  ylab("Indexed (1960=1)")
@
